Type-Safe Modular Parsing

### 2016-11-29 paper/sections/Overview.tex
Fix

  val pLam: (=> PackratParser[Expr]) => PackratParser[Expr] =
    e => "\\" ~> ident ~ ("." ~> e) ^^ { case x ~ b => Lam(x, b) }
  val pVarAppLam: (=> PackratParser[Expr]) => PackratParser[Expr] =
    e => pLam(e) | pVarApp(e)
}
\end{lstlisting}

>>>>

  val pLam: Fix[PackratParser[Expr]] =
    e => "\\" ~> ident ~ ("." ~> e) ^^ { case x ~ b => Lam(x, b) }
  val pVarAppLam: Fix[PackratParser[Expr]] =
    e => pLam(e) | pVarApp(e)
}
\end{lstlisting}
